%
% File: chap01.tex
% Author: ta16969
% Description: Introduction.
%
\let\textcircled=\pgftextcircled
\chapter{Introduction}
\label{chap:intro}

\initial{T}his chapter will serve as a contextual guide for the document. It introduces the project background and outlines the aims, objectives and overall structure of the document. The chapter concludes explaining the key areas of the project, structured as per the scope.


%=======
\section{Project Motivation}
\label{sec1:sec01}


The inspiration behind this project stems from the observation of a real world problem; Currently, incoming Computer Science (CS) cohorts at the University of Bristol (UoB) commence studies before the term officially starts via \textit{week zero} (W-0). W-0 is effectively a week long foundation skills development course before the commencement of the first official teaching block (TB-1).

The underlying objective of W-0 is commendable; It satisfies the necessity of orienting a technically and culturally diverse cohort to the main programming languages and procedural norms of the CS department at the UoB (from here on referred to as the CS department). However despite solving the aforementioned practical necessity for effective course delivery, W-0 is not without it shortcomings. Some examples are listed as follows:

\begin{itemize}

    \item W-0 overlaps with the Induction Week (IW) for UoB students which inevitably results in scheduling clashes. It can be reasonably deduced that scheduling clashes and student failure to attend either event compromises the underlying objectives of both IW and W-0.
    
    \item The CS department and the UoB both allocate resources towards W-0 and IW respectively. A deterioration in the underlying purpose of allocating these resources is arguably a wastage of limited teaching and administrative resources.
    
    \newpage
    
    \item W-0's traditional pedagogical delivery can not accommodate the individual learning needs of a technically diverse cohort from various academic and professional backgrounds; Effectively, W-0 does not make allowances for students to identify and address their own learning needs, at a time, place or mode that is convenient to them or allows them to personalize their learning experience.
    
    To illustrate this problem; A student with prior knowledge in the subject matter may wish to dedicate their resources elsewhere until TB-1 officially begins. Conversely those with insufficient learning experience or  resources may not be given the opportunity to reasonably address their learning needs to a standard expected of the cohort. Resultantlu compromised learning, student demotivation and failure are likely scenarios.
    
    \item Compromised learning and induction quality places undue costs on students and faculty; The very existence of IW and W-0 are indicative of a recognition of both teaching and learning needs that needs to be mitigated. To supplement the previous example; Teachers themselves may have to waste time repeating themselves again and again, despite troublesome subject matter being static; A shortcoming of a traditional classroom based pedagogy applicable to W-0 and otherwise.
    
    \item Despite the subject matter of W-0 being relatively static; the same traditional teaching resources need to be dedicated annually to execute it. This implies a process that can be optimised via a technological solution with either a non-recurrent or reduced allocation of resources. Alternatively an incrementally enriching TEL solution may be developed, that makes use of the recurrent allocation of resources i.e. improves over the long term with time and investment, as opposed to being a one-off teaching asset e.g. a class room lecture.
    
\end{itemize}




%==New Section
\section{Aims and Objectives}
\label{sec1:sec02}

The primary aim of the project is to create a Technology Enhanced Learning (TEL) solution, to substitute or complement existing traditional teaching delivery methods utilised by the CS programs at the UoB.

A secondary aim is also proposed to satisfy the problems cited in the Project Motivation section; the development of a TEL tool which may enable instructors to use modern pedagogical practices to improve learning outcomes and benefit students by giving them greater control over the learning process. Finally this project also aims for the TEL solution to be designed with the view of making it scalable and malleable, via open source considerations.

\newpage
The aims of this project will be realised by achieving the following objectives:

\begin{enumerate}

    \item Analysing and reviewing relevant literature, covering a multi-cognate spread of broad topics (explained in thesis scope \& structure) for the purpose of creating a strong theoretical foundation upon which to inspire the \textbf{creative} and \textbf{technical} design of the TEL solution. 
    
    \item Identifying the stakeholders of a TEL solution for the purpose of understanding stakeholders and their values. An understanding of stakeholder requirements and criteria will help temper the findings of secondary research and inspire the development of a holistic TEL solution, that will be successful and genuinely fit for purpose for its specific environment.
        
    \item Amalgamating the result of the aforementioned research and incorporating it into the creative and technical design of a TEL solution.
    
    \item Appropriately disseminating the code, developer notes,wikis and user manuals to make it open source so as to benefit scalability. In addition to this open source or collaborative user notes may also be created so as to enhance the efficacy of the TEL solution.
    
    \item Furthermore it is proposed that the project aims can be enhanced via the achievement of the following \textbf{optional objectives}:
    \begin{enumerate}
    \item Making technical and creative design considerations to benefit user accessibility and therefore the TEL solution's efficacy.
    \item Making technical design considerations to enhance applcation security and therefore make the technology more \textit{reliable} towards the benefit of users. As discussed later, enhancing the credibility or reliability of a TEL solution may improve its efficacy.
    \item Evaluating the TEL solution based on the creative and technical design considerations gained via research to design the TEL solution.
    \item Refactoring the code based on aforementioned user evaluation to improve the overall achievement of the design criterion
    \end{enumerate}
\end{enumerate}



\section{Added Value}
\label{sec:sec01}

It is envisioned that this project will contribute added value by:
\begin{itemize}
    \item Providing the CS faculty with a strategically advantageous option, to deliver curriculum elements via an modern asynchronous remote delivery method to reduce the reliance on traditional teaching resources that are one off investments to benefit from both administrative and learning advantages. E.g. Delegating mundane administrative elements or technically simple elements of the curriculum (a common theme in CS courses e.g. specific software to download, recommended IDE's and package managers, development environment options, etc) to the TEL tool and dedicating more time to complex aspects of the curriculum or even allocating more time to practical lab sessions.
    
    \item Remote delivery via the TEL tool may help to eliminate the need for a traditional W-0 and ultimately avoid scheduling clashes with IW, by delivering the curriculum either before IW starts or alternatively during IW but at a  convenient timing subject to IW schedules and student personal preferences.
    
    \item Improve the efficacy of learning objectives by giving students flexible and convenient asynchronous access to limited course or instructor content well before the start of the course. Students will be able to effectively gauge their development needs and prepare in advance as necessary, benefiting their personal development objectives.
    
    \item Provide a possible 'self-sift/taster' tool for the department's programmes so that students can assess whether the course is technically a good fit for them i.e. Students can consider in advance whether the course is indicative of desirable content and good teaching resources. This may benefit students by saving them resources and the departments administration by providing them with a possible sifting tool.
    
    \item May create a valuable HR resource by allowing staff to retrospectively assess their instruction delivery and develop junior staff (teaching assistants) by delegating TEL curriculum development and activities to them.
    
    \item May help create richer and niche course content by encouraging flexible input towards the curriculum by allowing students to share their own helpful curriculum resources, effectively improving course delivery over time.
    
    \item As the tool will be most likely Open Source in nature, it has the potential to create added value over time. It is envisioned that this may be enabled by allowing future UoB students to improve their TEL solution as per there own preferences or liking.
    
\end{itemize}








%==New Section

\section{Thesis Structure and Outline}
\label{sec1:sec04}

Given the predominant Type I nature of this project most of the work done is on implementation. Therefore the Type II research has been used to create a strong academic foundation to justify the theoretical underpinnings of the project undertaking, explaining the reason for the chosen modality i.e. A Social Network. The modality is justified by the desirable pedagogy it enables and ultimately benefits teaching and learning objectives.

The type II aspect of this report is used to inspire the creative and technical design of Artemis. Furthermore it is then used for the purposes of scoping evaluation and the resultant critical assessment. The resultant report is structured as follows:

\begin{itemize}

\item\textbf{Chapter 02 - TEL \& Pedagogy}:

This chapter shall explore and identify the relationship between appropriate pedagogies and a successful TEL solution, the latter an enabler for the former. Based on this a social network is identified and justified as an appropriate TEL solution out of the many possible modalities. Furthermore this chapter will identify creative design criteria for the solution, possible stakeholders and illustrate a use case via the lens of \textit{participatory learning}. The underlying rationale for selecting an Open Source and an Open Educational Resource (OER)  solution will also be identified here.


\item\textbf {Chapter 03 - Captology, Web Application Security and User Accessibility}:

This chapter shall pivot towards the practical and technical implications of developing the TEL solution as a web application. Relevant best practice for persuasive web application design,web credibility, accessibility and security is identified. This shall ultimately form the basis for refining implementation, evaluation and critical review of the project. The technical criteria resulting from this chapter have been used to polish the application for the  purpose of a successful deployment if desired.


\item\textbf {Chapter 04 - Implementation and Features}:

As the title suggests, this chapter covers the implementation details of Artemis and it's key features. It also includes notes on relevant stakeholder feedback (identified in Chapter 02), that inspired the creative features of the project and it's dissemination as an Open Source OER.

\item\textbf {Chapter 05 - Evaluation and Refactoring}:

The chapter explains how Artemis was evaluated from the Lens of Web Credibility and then subsequently audited and re-factored for accessibility, user experience and security. 

\item\textbf {Chapter 06 - Critical Review and Conclusion}:

The chapter concludes the project with a critical review of Artemis and a future roadmap.

\end{itemize}



%=========================================================